Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Implies That Modelling This Situation Using Other Models Would Be Better

### 2024-12-13 paper/paper.qmd
Render the pdf

# Load the necessary packages
library(tidyverse)
library(opendatatoronto)
library(janitor)
library(dplyr)
library(readr)
library(knitr)
library(kableExtra)
library(arrow)
library(ggplot2)

@@

# Refit the model with the transformed Y
new_model <- lm(count_transformed ~ service_type + program_area + classification + capacity +
                  occupancy_rate + capacity:occupancy_rate, data = analysis_data)

@@

>>>>

# Load the necessary packages
library(tidyverse)
library(opendatatoronto)
library(janitor)
library(dplyr)
library(readr)
library(knitr)
library(kableExtra)
library(arrow)
library(ggplot2)
library(MASS)

@@

# Refit the model with the transformed Y
new_model <- lm(count_transformed ~ service_type + program_area + classification + capacity +
                  occupancy_rate + capacity:occupancy_rate, data = cleaned_data2)

@@

residuals_df_new <- data.frame(
  res = res_new,
  theoretical = qnorm(ppoints(length(res_new))
  )
)
